\documentclass{article}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{booktabs}
\usepackage[scr=boondox]{mathalpha}
\usepackage{mathtools}
\usepackage{mleftright}
\usepackage{parskip}
\usepackage{physics}
\usepackage{times}
\usepackage{url}
\usepackage{xcolor}
\usepackage{xparse}

\algrenewcomment[1]{{$\triangleright$\text{\ }\textit{#1}}}
\setcounter{MaxMatrixCols}{30}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{notation}{Notation}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{claim}{Claim}
\newtheorem{remark}{Remark}

\makeatletter
\def\thm@space@setup{\thm@preskip=\parskip \thm@postskip=0pt}
\makeatother

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\E}{\mathbb{E}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}

\title{SUTD 404}
\author{
	Gregory Lim,
	Edison Ang,
	Manishansh Shaswat,
	Muthu Ramaswamy
}
\date{April 2026}

\begin{document}

\maketitle

\section{Introduction}

The Singapore University of Technology and Design (SUTD) has over 200 rooms split across 5 buildings.
To help people (especially visitors) find rooms,
each room is assigned an address of the form
$\texttt{x.y-z}$,
where $\texttt{x}$ is a building number,
$\texttt{y}$ is a floor number,
and $\texttt{z}$ is a room number.
However, resources that aim to map rooms to addresses remain few and far between.
Physical resources like campus signs exist, but require one to walk around, expending lots of energy and time.
Digital resources like the SUTD Assistive Maps (SAM) Telegram bot exist, but are often arduous to maintain and less robust to noise like typos (which can be especially pertinent for visitors who do not often type in English).
To fill this gap, we built SUTD 404, a digital resource that aims to maps rooms to addresses in a way that learns over time and handles noise gracefully.
Our GitHub repository can be found at \url{gregorylimeurhen/sutd404}.

\newpage

\section{Methodology}

% Read comments for developer (i.e. implementation) prose not in the paper please!
% For brevity, we call a room name a "room", and a room address an "address"
% Henceforth:
% - all ties shall be broken uniform randomly, if any
% - stuff (e.g. columns, keys, rows, values, etc.) shall be sorted lexicographically, if any

Let $V$ be a vocabulary,
and $R\subseteq V^{*}$ be a room set,
and $A\subseteq V^{*}$ be an address set,
and $B\subseteq V$ be a boundary set,
and $C\in\N$ be a corruption count,
and $\alpha\in\R_{[0,1]}$ be a transposition rate,
and $\beta\in\R_{[0,1]}$ be a substitution rate,
and $\bm{\pi}=(\pi_\mathrm{train},\pi_\mathrm{val},\pi_\mathrm{test})\in\Delta^{2}$ be a training-validation-testing split,
and $I:V\rightharpoonup\Z^{2}$ be a keyboard-position map,
and $C\bm{\pi}\in\N^{3}$,
and each tie be broken uniform randomly.

\begin{definition}[Keyboard]
$${\setlength{\arraycolsep}{2pt}
	K
	=
	\begin{bmatrix}
		\texttt{`} & & \texttt{1} & & \texttt{2} & & \texttt{3} & & \texttt{4} & & \texttt{5} & & \texttt{6} & & \texttt{7} & & \texttt{8} & & \texttt{9} & & \texttt{0} & & \texttt{-} & & \texttt{=}
		\\
		\texttt{q} & & \texttt{w} & & \texttt{e} & & \texttt{r} & & \texttt{t} & & \texttt{y} & & \texttt{u} & & \texttt{i} & & \texttt{o} & & \texttt{p} & & \texttt{[} & & \texttt{]} & & \verb|\|
		\\
		& & \texttt{a} & & \texttt{s} & & \texttt{d} & & \texttt{f} & & \texttt{g} & & \texttt{h} & & \texttt{j} & & \texttt{k} & & \texttt{l} & & \texttt{;} & & \texttt{'} & &
		\\
		& & & \texttt{z} & & \texttt{x} & & \texttt{c} & & \texttt{v} & & \texttt{b} & & \texttt{n} & & \texttt{m} & & \texttt{,} & & \texttt{.} & & \texttt{/} & & & &
		\\
		& & & & & & & & & & \textvisiblespace & \textvisiblespace & \textvisiblespace & \textvisiblespace & \textvisiblespace & & & & & & & & & &
	\end{bmatrix}
}$$
\end{definition}

Our keyboard uses the 60\% ANSI QWERTY en-US keyboard layout without backspace, tab, caps lock, enter, shift, ctrl, alt, and system keys.
All keys have equal padding between them.

\begin{algorithm}[H]
	\caption{$\textsc{Corrupt}(\bm{x})$}
	\begin{algorithmic}
		\Require $\bm{x}\in V^{*}$
		\State ${
			(T_{L},T_{M},T_{R})
			\gets
			(\{\bm{\epsilon}\}\cup V^{*}B,(V\setminus B)^{+},\{\bm{\epsilon}\}\cup BV^{*})
		}$
		\State ${
			T
			\gets
			\{
				\bm{u}\bm{w}b\bm{v}\bm{z}
				\mid
				\bm{u}\in T_{L},\,
				\bm{v},\bm{w}\in T_{M},\,
				\bm{z}\in T_{R},\,
				b\in B,\,
				\bm{x}=\bm{u}\bm{v}b\bm{w}\bm{z}
			\}
			\setminus
			\{\bm{x}\}
		}$
		\If{$T\neq\varnothing$}
			${\bm{x}\sim\alpha\,\mathcal{U}(T)+(1-\alpha)\,\delta(\bm{x})}$
		\EndIf
		\For{$i\in[1..\abs{\bm{x}}]$}
			\State $S\gets\{k\in K\setminus \{x_{i}\}\mid I(k)-I(x_{i})\in[-1..1]\times[-2..2]\}$
			\If{$S\neq\varnothing$}
				${x_{i}\sim\beta\,\mathcal{U}(S)+(1-\beta)\,\delta(x_{i})}$
			\EndIf
		\EndFor
		\State \Return $\bm{x}$
	\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
	\caption{$\textsc{Split}()$}
	\begin{algorithmic}
		\State $(D_\mathrm{train},D_\mathrm{val},D_\mathrm{test})\gets(\varnothing,\varnothing,\varnothing)$
		\For{$r\in R$}
			\State $P\gets\varnothing$
			\While{$\abs{P}<C$}
				\State $r'\sim\textsc{Corrupt}(r)$
				\If{$r'\neq r$}
					$P\gets P\cup\{(r',r)\}$
				\EndIf
			\EndWhile
			\State $P_\mathrm{train}\sim\mathcal{U}(\{Q\subseteq P\mid \abs{Q}=\pi_\mathrm{train}C\})$
			\State $P_\mathrm{val}\sim\mathcal{U}(\{Q\subseteq P\setminus P_\mathrm{train}\mid \abs{Q}=\pi_\mathrm{val}C\})$
			\State $P_\mathrm{test}\gets P\setminus(P_\mathrm{train}\cup P_\mathrm{val})$
			\State ${
				(D_\mathrm{train},D_\mathrm{val},D_\mathrm{test})
				\gets
				(
					D_\mathrm{train}\cup P_\mathrm{train},
					D_\mathrm{val}\cup P_\mathrm{val},
					D_\mathrm{test}\cup P_\mathrm{test}
				)
			}$
		\EndFor
		\State \Return $(D_\mathrm{train},D_\mathrm{val},D_\mathrm{test})$
	\end{algorithmic}
\end{algorithm}

We set $C=50$, and $\alpha=0.5$, and $\beta=0.05$, and $\bm{\pi}=(0.8,0.1,0.1)$.
Our corruption algorithm corrupts strings by transposing spans and substituting characters.
First, the algorithm samples whether to transpose spans by uniformly sampling from the space of span transpositions.
Then, for each character in the string, the algorithm samples whether to substitute the character by uniformly sampling from the space of character substitutions.
This space contains nearby characters collected by sliding a window of height $3$ and width $5$ centred at each position in $K$.
Finally, the algorithm returns the corrupted string.
The algorithm terminates on our hyperparameter choices.

\begin{definition}[Denoiser]
Let $f:V^{*}\times R\to\R$ be a scorer.
\begin{align*}
	\mathscr{D}_{f}
	&:
	V^{*}\to R
	\\
	\mathscr{D}_{f}(x)
	&=
	\argmax_{r\in R}
	f(x,r)
\end{align*}
\end{definition}

\begin{definition}[Lookup]
$$
	\mathscr{L}:R\to A
$$
\end{definition}

% Edges map rooms to their addresses in the untouched `edges.tsv`
% Because a room like `foo` can have multiple addresses like `A, B`,
% we write a script `preprocess.py` to:
% 1. generate `train.tsv` (for D_train), `val.tsv` (for D_val), `test.tsv` (for D_test)
% by writing `corrupted	normal` pairs as rows
% 2. convert `edges.tsv` to `n2a.tsv` with each row like `foo	A, B`
% so look-up for `foo` yields `A, B`
% The data is thus fixed after preprocessing

Our denoiser is a standard Nanochat-parameterised transformer of depth $2$ with character-level tokenisation. % cite karpathy/nanochat
We use character-level tokenisation as typos are often character-level, and room names are short enough for individual characters to be highly meaningful semantic units for our task.
We use a standard cross-entropy loss and AdamW optimiser.
A complete list of hyperparameters can be found in our GitHub repository.
Our lookup is a standard key-value map from rooms to addresses.

% Search the web for https://github.com/karpathy/nanochat
% Everything is clean, default, and standard with no other stuffs:
% - Training loss applied only to clean (target) portion
% - Adam on default settings
% - Batch size derivable as largest batch that fits in memory
% - Seed 1
% - Nothing else, no dropout or whatever
% We log to our `wandb` account

\begin{algorithm}[H]
	\caption{$\textsc{Infer}(f,x)$}
	\begin{algorithmic}
		\Require $f:V^{*}\times R\to\R$, $x\in V^{*}$
		\If{$x\not\in R$}
			$x\gets\mathscr{D}_{f}(x)$
		\EndIf
		\State $x\gets\mathscr{L}(x)$
		\State \Return $x$
	\end{algorithmic}
\end{algorithm}

Our inference algorithm receives a scorer and string as input.
First, the algorithm denoises the string to a room using the scorer if the string is not a room.
Then, the algorithm looks up the address of the room.
Finally, the algorithm returns the address.

\newpage

\section{Experimentation}

Keeping the hardware and rest of the system fixed, we evaluated our denoiser against Levenshtein distance, Damerau--Levenshtein distance (DL), longest common subsequence length (LCS), and character histogram intersection (CH) denoisers,
measuring the accuracy and mean latency of each denoiser on the test set.
% We display the results with more natural units and scale, for your perusal

\begin{table}[H]
	\centering
	\caption{Summary.}
	\begin{tabular}{lll}
		\toprule
		Denoiser & Accuracy (\%) & Mean Latency (ms) \\
		\midrule
		L & 72.5 & 9.05 \\
		DL & 71.9 & 16.8 \\
		LCS & 59.2 & 5.38 \\
		CH & 37.1 & \textbf{0.289} \\
		Ours & \textbf{97.3} & 7.88 \\
		\bottomrule
	\end{tabular}
\end{table}

L captures insertions, deletions, and substitutions.
DL extends L by capturing adjacent transpositions.
LCS and CH capture ordered and unordered character overlap respectively.
Accuracy was measured using the fraction of test inputs for which final address equals gold address.
Mean latency was measured using the mean time taken to get an output from giving an input.

\newpage

\section{Deployment}

We deployed SUTD 404 as web application served at \url{sutd404.vercel.app}.

\begin{algorithm}[H]
	\caption{$\textsc{Predict}(x)$}
	\begin{algorithmic}
		\Require $x\in V^{*}$
		\State $x\gets\textsc{Strip}(x)$
		\State $x\gets\textsc{Lowercase}(x)$
		\State $x\gets\textsc{AlphanumericSplit}(x)$
		\State $x\gets\textsc{Alias}(x)$
		\If{$x\in R$}
			\Return $(x,\mathscr{L}(x))$
		\EndIf
		\State ${
			O
			\gets
			\bigcup_{
				f
				\in
				\{
					\textsc{L},
					\textsc{DL},
					\textsc{LCS},
					\textsc{CH},
					\textsc{Ours}
				\}
			}
			\arg\operatorname{top}_{r\in R}^{(2)}f(x,r)
		}$
		\State $O\gets\{(o,\mathscr{L}(o))\mid o\in O\}$
		\State $O\gets\textsc{LexicographicSort}(O)$
		\State \Return $O$
	\end{algorithmic}
\end{algorithm}

Our prediction algorithm uses all denoisers in parallel as they have comparable latencies on millisecond timescales and are able to cover each others' weaknesses.

\end{document}
